%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape John W. Novak} \\ \vspace{3pt}
    \small \faIcon{phone-square-alt} (484) 619-1783 $|$ \href{mailto:johnwnovak1@gmail.com}{\faIcon{envelope} \text{johnwnovak1@gmail.com}} $|$ 
    \href{https://linkedin.com/in/johnnovaktu/}{\faIcon{linkedin} \text{johnnovaktu}} $|$
    \href{https://github.com/jnovak96}{\faIcon{github} \text{jnovak96}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Software Developer}{November 2022 -- Present}
        {B Braun Medical Inc. -- R\&D Active Devices}{Allentown, PA}
        \resumeItemListStart
          \resumeItem{Developed a software application for tracking and monitoring an automated IV pumps on an enterprise scale, significantly alleviating workload of nurses and hospital staff, using .NET, Angular, Microsoft SQL Server.}
          \resumeItem{Significantly improved code quality of application and unit test coverage.}
          \resumeItem{Was one of 2 developers tasked with building a web application to fully simulate real IV pump hardware and interface with main application.}
          \resumeItem{Item 4}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer - Contractor}{February 2022 -- October 2022}
      {Barnegat Bay Capital Management}{Summit, NJ}
      \resumeItemListStart
        \resumeItem{Worked with owner to develop solutions to significantly speed up and automate financial analytical processes.}
.       \resumeItem{Developed software solutions in Python to and interface with financial APIs to provide performance metrics on hundreds of small to large cap ETFs.}
        \resumeItem{Significantly improved client's Microsoft Excel workflow by providing custom VBA macros to automate various mathematical and formatting requirements.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Freelance Web Developer}{January 2022 -- Present}
      {Various Clients}{Bethlehem, PA}
      \resumeItemListStart
        \resumeItem{Added new functionality to existing websites such as file uploading, comment section, and user login functionality.}
        \resumeItem{Utilized PostgreSQL and MySQL databases with over 5000 data entries and handled database processes with secure and efficient back-end code.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{AI Deep Learning Face Mask Detector} $|$ \emph{Python, PyTorch, Pandas, Numpy}}{April 2021 -- June 2021}
          \resumeItemListStart
            \resumeItem{Built a program that uses deep learning technology capable of discerning images where N95 masks are being worn on a human face against images of faces without masks with over 90\% accuracy.}
            \resumeItem{Written in Python using PyTorch convolutional neural network trained with a public dataset of over 4000 images.}
            \resumeItem{Tweaked neural network architecture over time by optimizing layers, transforms and kernel size to improve results.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{URP/SSP Student Research Success Tracker} $|$ \emph{ASP.Net, C\#, MySQL, JQuery}}{November 2020 -- April 2021}
          \resumeItemListStart
            \resumeItem{Collaborated with a team to write a web application to automate about 80\% of school research tracking workload.}
            \resumeItem{Handled thousands of research projects, students, and PIs on a relational SQL database using secure and well-tested stored procedures and back-end C\# code.}
            \resumeItem{Built a custom comment system, file upload system, and user login with multiple user types and session handling.}
            \resumeItem{Provided code and detailed documentation on over 50 custom API functions.}
            \resumeItem{Worked in an agile environment with scrums, progress reports, and requirement documentation.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Custom Feature-Rich Shell/Command Line} $|$ \emph{C, Linux, gcc, gdb}}{September 2018 -- January 2019}
          \resumeItemListStart
            \resumeItem{Programmed a Unix shell / command line in C that uses the GNU / Linux glibc library for filesystem functions.}
            \resumeItem{Was capable of changing directories, copying files, executing processes with multithreading, and piping process outputs}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, Python, C/C++, Java, SQL (PostgreSQL/MySQL), JavaScript, PHP, XML, JSON, HTML/CSS} \\
     \textbf{Frameworks}{: ASP.Net, Spring, Angular, React, Node.js, JQuery, Bootstrap} \\
     \textbf{Developer Tools}{: Git, Docker, Visual Studio, Microsoft Azure, PyCharm, Linux CL, Vim, gcc, gdb} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, PyTorch, OpenCV, OpenGL, glibc}
    }}
 \end{itemize}

 
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Temple University}{Philadelphia, PA}
      {Bachelor of Science in Information Science and Technology, Minor in Computer Science}{Graduated Dec 2021}
  \resumeSubHeadingListEnd



% %-------------------------------------------
% \section{Interests}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{Robotics, Arduino, Linux, video game emulation, 3D graphics programming, machine learning } \\
%     }
%  \end{itemize}
\end{document}
